Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-08-05 Paper/Manuscript_Stats&Comp/reply_letter_2nd_STCO.tex
Minor edits to reply letter

\item We have revised the entire manuscript making some minor edits, such as rewriting a few sentences and adding minor little additional information.

@@

Based on the evidence that we have at this point, we can unfortunately not give evidence-based suggestions as to when to stop pre-convergence and try something else because we have seen only very few iterations to be required in all the investigated cases. With regard to high-dimensional cases, the main problem would not be more iterations (as far as we have seen) but the computational cost of each iteration. More concretely, as we discuss in detail in the paper, the more input dimensions ($D$) we have, the more multivariate basis functions we get ($m^*=nm^D$, with $n$=number of points and $m$=number of univariate basis functions), which affects the HMC sampling of a model fit (per iteration), but not (in a relevant manner) the number of iterations required to complete the diagnostic procedure. We have now clarified these points at the end of Section 4.5.1.

>>>>

\item We have revised the entire manuscript making several minor edits, such as rewriting a few sentences and adding minor additional information.

@@

Based on the evidence that we have at this point, we can unfortunately not give evidence-based suggestions as to when to stop pre-convergence and try something else because we have seen only very few iterations to be required in all the investigated cases. With regard to high-dimensional cases, the main problem would not be more iterations (as far as we have seen) but the computational cost of each iteration. More concretely, as we discuss in detail in the paper, the more input dimensions ($D$) we have, the number of required multivariate basis functions increases ($m^*=nm^D$, with $n$=number of points and $m$=number of univariate basis functions), which affects the HMC sampling of a model fit (per iteration), but not (in a relevant manner) the number of iterations required to complete the diagnostic procedure. We have now clarified these points at the end of Section 4.5.1.
